The effects of ongoing context inference on motor learning

### 2021-11-11 adaptation/article/article.tex
Finalized. Submitted to Nat.Comm.

% Remember to start reftex-mode
\bibliographystyle{ieeetr}

@@

\title{The effects of ongoing context inference on motor learning}
\shorttitle{Context-inference-dependent motor learning}
\author[1,2]{Cuevas Rivera, Darío}
\author[1,2]{Kiebel, Stefan J.}
\affil[1]{Chair of Neuroimaging, Faculty of Psychology, Technische Universität Dresden, 01062 Dresden, Germany.}
\affil[2]{Centre for Tactile Internet with Human-in-the-Loop (CeTI)}
\affiliation{~}

@@

\section{Acknowledgment}
Funded by the German Research Foundation (DFG, Deutsche Forschungsgemeinschaft) as part of Germany’s Excellence Strategy – EXC 2050/1 – Project ID 390696704 – Cluster of Excellence “Centre for Tactile Internet with Human-in-the-Loop” (CeTI) of Technische Universität Dresden.

\bibliography{MyLibrary}

>>>>

% Remember to start reftex-mode

@@

\title{The effects of ongoing context inference on motor learning}
\shorttitle{Context-inference-dependent motor learning}
% \author[1,2]{Cuevas Rivera, Darío}
% \author[1,2]{Kiebel, Stefan J.}
% \affil[1]{Chair of Neuroimaging, Faculty of Psychology, Technische Universität Dresden, 01062 Dresden, Germany.}
% \affil[2]{Centre for Tactile Internet with Human-in-the-Loop (CeTI)}
\author[1]{Author list}
\affil[1]{Affiliation list}
\affiliation{~}

@@

% \section{Acknowledgment}
% Funded by the German Research Foundation (DFG, Deutsche Forschungsgemeinschaft) as part of Germany’s Excellence Strategy – EXC 2050/1 – Project ID 390696704 – Cluster of Excellence “Centre for Tactile Internet with Human-in-the-Loop” (CeTI) of Technische Universität Dresden.

\bibliography{../../MyLibrary}
